The contact value approach for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-06-25 papers/pair-correlation/paper.tex
experiment with a higher-order fit specifically to the same range as Gil Villegas Tested on bennet. Took 0:23.24.

\begin{document}
\title{The contact value approximation for the pair distribution function of the inhomogeneous hard-sphere
  fluid}

@@

>>>>

\begin{document}
\title{The contact value approach for the pair distribution function of the inhomogeneous hard-sphere
  fluid}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/short-range-ghs-alt}
  \caption{Plot of the hard-sphere radial distribution function, with
    our short-range separable
    fit.}\label{fig:short-range-radial-distribution}
\end{figure}
